Staged Abstract Interpreters

### 2019-02-22 paper/10_intro.tex
typo

Now we have seen two orthogonal transformations of interpreters: by
speclization, we can refactor interpreters to code generators; by abstraction,
we can refactor interpreters to static analyzers. As an intellectual quest, it
is natural to ask --- starting from an interpreter, \textbf{can we derive a
sound abstract interpreter but it works like a code generator which produces fast
analysis code?} Conceptually, it is similar to the concrete setting: for an
abstract interpreter $\widehat{\texttt{eval}}: \texttt{Expr} \to
\widehat{\texttt{Env}} \to \widehat{\texttt{Value}}$, which takes a program, an abstract
environment and returns abstract values, we would like to specialize it with
repsect to a program $e_0$ and produce an code generator
$\widehat{\texttt{eval}}_{\texttt{e0}} : \widehat{\texttt{Env}} \to
\widehat{\texttt{Value}}$, such that $
\widehat{\texttt{eval}}_{\texttt{e0}}(\widehat{\rho}) =
\widehat{\texttt{eval}}(e_0)(\widehat{\rho})$, but the staged one leaves the
abstract environment $\widehat{\rho}$ dynamic.

>>>>

Now we have seen two orthogonal transformations of interpreters: by
specliazation, we can refactor interpreters to code generators; by approximation,
we can refactor interpreters to static analyzers. As an intellectual quest, it
is natural to ask --- starting from an interpreter, \textbf{can we derive a
sound abstract interpreter but it works like a code generator which produces fast
analysis code?} Conceptually, it is similar to the concrete setting: for an
abstract interpreter $\widehat{\texttt{eval}}: \texttt{Expr} \to
\widehat{\texttt{Env}} \to \widehat{\texttt{Value}}$, which takes a program, an abstract
environment and returns abstract values, we would like to specialize it with
repsect to a program $e_0$ and produce an code generator
$\widehat{\texttt{eval}}_{\texttt{e0}} : \widehat{\texttt{Env}} \to
\widehat{\texttt{Value}}$, such that $
\widehat{\texttt{eval}}_{\texttt{e0}}(\widehat{\rho}) =
\widehat{\texttt{eval}}(e_0)(\widehat{\rho})$, but the staged one leaves the
abstract environment $\widehat{\rho}$ dynamic.
